Errata

### 2025-04-08 tex/Manuscript-3.tex
Update manuscript files with chapter marks and improve section formatting for clarity
Add titles to figures and tables

\chapter{Microbial impact on initial soil formation in arid and semiarid environments under simulated climate change}

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=1\textwidth]{img/M3-Figure_1.jpg}
	\caption{Sampling sites and microcosms of Pan de Azúcar and Santa Gracia after 12 weeks of incubation. The different microcosms are separated by horizon and treatment, including in situ, BSC (Biocrust), and plant treatment.}
	\label{fig:M3-F1}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=1\textwidth]{img/M3-Figure_2.jpg}
	\caption{Physicochemical properties in Pan de Azúcar (PA) and Santa Gracia (SG) show total organic carbon (TOC), nitrogen in bulk soil (Nbulk), pH, electrical conductivity (EC), and mean weight diameter (MWD) in three-time points of the soil manipulation experiment. Time is represented by T0 (original soil sample), T1 (2 weeks), and T3 (16 weeks). Different colors represent the different treatments. Each bar is the mean of biological triplicates.}
	\label{fig:M3-F2}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=1\textwidth]{img/M3-Figure_3.jpg}
	\caption{Gene copy numbers, Shannon index, and Evenness of bacterial communities in Pan de Azúcar (PA) and Santa Gracia (SG) in four soil manipulation experiment time points. Time is represented by T0 (original), T1 (2 weeks), T2 (12 weeks), and T3 (16 weeks). Different colors represent the different treatments. Each bar is the mean of biological triplicates.}
	\label{fig:M3-F3}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=1\textwidth]{img/M3-Figure_4.jpg}
	\caption{Distance-based redundancy analysis (dbRDA) including soil properties for Pan de Azúcar - A horizon, Pan de Azúcar - B horizon, Santa Gracia - A horizon, and Santa Gracia - B horizon. Significant physicochemical properties included total organic carbon (TOC), nitrogen in macroaggregates (Nt 250), nitrogen in large microaggregates (Nt 250-53), nitrogen in small microaggregates (Nt 53), pH, electrical conductivity (EC), sodium, mean weight diameter (MWD), total carbon in macroaggregates (Ct 250), total carbon in small microaggregates (Ct 53). Time is represented by T0 (original soil sample), T1 (2 weeks), and T3 (16 weeks). Different color represents different treatments, while shapes represent different sampling times. Each point is the mean of biological triplicates.}
	\label{fig:M3-F4}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=1\textwidth]{img/M3-Figure_5.jpg}
	\caption{Relative abundance of top 15 bacterial phyla for Pan de Azúcar and Santa Gracia in four-time points of the soil manipulation experiment. Time is represented as T0 (original), T1 (2 weeks), T2 (12 weeks), and T3 (16 weeks). Each bubble is the mean of the different treatments (in situ, BSCs, and plants) and biological triplicates.}
	\label{fig:M3-F5}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=1\textwidth]{img/M3-Figure_6.jpg}
	\caption{Top 50 relative abundance of indicator species for Pan de Azúcar and Santa Gracia in four time points of the soil manipulation experiment. Colors represented different phyla. Time is represented as T0 (original), T1 (2 weeks), T2 (12 weeks), and T3 (16 weeks). Each bubble is the mean of the different treatments (in situ, BSCs, and plants) and biological triplicates. Taxa are shown on the level of class (c), order (o), family (f), and genus (g).}
	\label{fig:M3-F6}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=1\textwidth]{img/M3-Figure_7.jpg}
	\caption{Co-occurrence network of bacterial ASVs. The nodes (ASVs) in the network are colored by modularity. The connections stand for a strong (R > 0.7) and significant (p < 0.01) correlation. The network was subdivided into two subnetworks corresponding to Pan de Azúcar and Santa Gracia.}
	\label{fig:M3-F7}
\end{figure}

\begin{table}[ht]
	\centering
	\caption{Co-occurrence network topological metrics.}
	\label{tab:M3-T1}
	\begin{tabular}{lcc}
	\hline
	\textbf{Network metrics} & \textbf{Pan de Azúcar} & \textbf{Santa Gracia} \\
	\hline
	No. of nodes\textsuperscript{1} & 185 & 88 \\
	No. of edges\textsuperscript{2} & 2,054 & 1,149 \\
	Average degree\textsuperscript{3} & 11.1 & 13.02 \\
	Cluster coefficient\textsuperscript{4} & 0.639 & 0.798 \\
	Modularity\textsuperscript{5} & 0.589 & 0.429 \\
	Connectance\textsuperscript{6} & 0.060 & 0.148 \\
	\hline
	\end{tabular}

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=1\textwidth]{img/M3-Figure_8.jpg}
	\caption{
	Pearson correlation of modules from the co-occurrence network and soil physicochemical properties in Pan de Azúcar (PA) and Santa Gracia (SG). Only correlations greater than $R = 0.5$ are shown. Significance levels are indicated as follows: ``\textbf{**}'' for $p < 0.01$ and ``\textbf{***}'' for $p < 0.001$.
	The physicochemical properties included nitrogen in the bulk soil (N\textsubscript{bulk}), total organic carbon (TOC), total mass in macroaggregates (Mass 250), total mass in large microaggregates (Mass 250--53), total mass in small microaggregates (Mass 53), mean weight diameter (MWD), total carbon in macroaggregates (Ct 250), total carbon in large microaggregates (Ct 250--53), total carbon in small microaggregates (Ct 53), nitrogen in macroaggregates (Nt 250), nitrogen in large microaggregates (Nt 250--53), nitrogen in small microaggregates (Nt 53), sodium, potassium, chloride, nitrate, sulfate, pH, and electrical conductivity (EC).
	}
	\label{fig:M3-F8}
\end{figure}

>>>>

\chapter{Microbial impact on initial soil formation in arid and semiarid environments under simulated climate change}
\chaptermark{Manuscript 3}

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=1\textwidth]{img/M3-Figure_1.jpg}
	\caption[Sampling sites and microcosms of Pan de Azúcar and Santa Gracia after 12 weeks of incubation]{Sampling sites and microcosms of Pan de Azúcar and Santa Gracia after 12 weeks of incubation. The different microcosms are separated by horizon and treatment, including in situ, BSC (Biocrust), and plant treatment.}
	\label{fig:M3-F1}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=1\textwidth]{img/M3-Figure_2.jpg}
	\caption[Physicochemical properties in Pan de Azúcar and Santa Gracia]{Physicochemical properties in Pan de Azúcar (PA) and Santa Gracia (SG) show total organic carbon (TOC), nitrogen in bulk soil (Nbulk), pH, electrical conductivity (EC), and mean weight diameter (MWD) in three-time points of the soil manipulation experiment. Time is represented by T0 (original soil sample), T1 (2 weeks), and T3 (16 weeks). Different colors represent the different treatments. Each bar is the mean of biological triplicates.}
	\label{fig:M3-F2}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=1\textwidth]{img/M3-Figure_3.jpg}
	\caption[Gene copy numbers, Shannon index, and Evenness of bacterial communities in Pan de Azúcar and Santa Gracia in four soil manipulation experiment time points]{Gene copy numbers, Shannon index, and Evenness of bacterial communities in Pan de Azúcar (PA) and Santa Gracia (SG) in four soil manipulation experiment time points. Time is represented by T0 (original), T1 (2 weeks), T2 (12 weeks), and T3 (16 weeks). Different colors represent the different treatments. Each bar is the mean of biological triplicates.}
	\label{fig:M3-F3}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=1\textwidth]{img/M3-Figure_4.jpg}
	\caption[Distance-based redundancy analysis (dbRDA) including soil properties for A and B soil horizons in Pan de Azúcar and Santa Gracia]{Distance-based redundancy analysis (dbRDA) including soil properties for Pan de Azúcar - A horizon, Pan de Azúcar - B horizon, Santa Gracia - A horizon, and Santa Gracia - B horizon. Significant physicochemical properties included total organic carbon (TOC), nitrogen in macroaggregates (Nt 250), nitrogen in large microaggregates (Nt 250-53), nitrogen in small microaggregates (Nt 53), pH, electrical conductivity (EC), sodium, mean weight diameter (MWD), total carbon in macroaggregates (Ct 250), total carbon in small microaggregates (Ct 53). Time is represented by T0 (original soil sample), T1 (2 weeks), and T3 (16 weeks). Different color represents different treatments, while shapes represent different sampling times. Each point is the mean of biological triplicates.}
	\label{fig:M3-F4}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=1\textwidth]{img/M3-Figure_5.jpg}
	\caption[Relative abundance of top 15 bacterial phyla for Pan de Azúcar and Santa Gracia in four-time points of the soil manipulation experiment]{Relative abundance of top 15 bacterial phyla for Pan de Azúcar and Santa Gracia in four-time points of the soil manipulation experiment. Time is represented as T0 (original), T1 (2 weeks), T2 (12 weeks), and T3 (16 weeks). Each bubble is the mean of the different treatments (in situ, BSCs, and plants) and biological triplicates.}
	\label{fig:M3-F5}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=1\textwidth]{img/M3-Figure_6.jpg}
	\caption[Top 50 relative abundance of indicator species for Pan de Azúcar and Santa Gracia in four time points of the soil manipulation experiment]{Top 50 relative abundance of indicator species for Pan de Azúcar and Santa Gracia in four time points of the soil manipulation experiment. Colors represented different phyla. Time is represented as T0 (original), T1 (2 weeks), T2 (12 weeks), and T3 (16 weeks). Each bubble is the mean of the different treatments (in situ, BSCs, and plants) and biological triplicates. Taxa are shown on the level of class (c), order (o), family (f), and genus (g).}
	\label{fig:M3-F6}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=1\textwidth]{img/M3-Figure_7.jpg}
	\caption[Co-occurrence network of bacterial ASVs]{Co-occurrence network of bacterial ASVs. The nodes (ASVs) in the network are colored by modularity. The connections stand for a strong (R > 0.7) and significant (p < 0.01) correlation. The network was subdivided into two subnetworks corresponding to Pan de Azúcar and Santa Gracia.}
	\label{fig:M3-F7}
\end{figure}

\begin{table}[ht]
	\centering
	\caption[Co-occurrence network topological metrics]{Co-occurrence network topological metrics.}
	\label{tab:M3-T1}
	\begin{tabular}{lcc}
	\hline
	\textbf{Network metrics} & \textbf{Pan de Azúcar} & \textbf{Santa Gracia} \\
	\hline
	No. of nodes\textsuperscript{1} & 185 & 88 \\
	No. of edges\textsuperscript{2} & 2,054 & 1,149 \\
	Average degree\textsuperscript{3} & 11.1 & 13.02 \\
	Cluster coefficient\textsuperscript{4} & 0.639 & 0.798 \\
	Modularity\textsuperscript{5} & 0.589 & 0.429 \\
	Connectance\textsuperscript{6} & 0.060 & 0.148 \\
	\hline
	\end{tabular}

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=1\textwidth]{img/M3-Figure_8.jpg}
	\caption[Pearson correlation of modules from the co-occurrence network and soil physicochemical properties in Pan de Azúcar and Santa Gracia]{Pearson correlation of modules from the co-occurrence network and soil physicochemical properties in Pan de Azúcar (PA) and Santa Gracia (SG). Only correlations greater than $R = 0.5$ are shown. Significance levels are indicated as follows: ``\textbf{**}'' for $p < 0.01$ and ``\textbf{***}'' for $p < 0.001$.
	The physicochemical properties included nitrogen in the bulk soil (N\textsubscript{bulk}), total organic carbon (TOC), total mass in macroaggregates (Mass 250), total mass in large microaggregates (Mass 250--53), total mass in small microaggregates (Mass 53), mean weight diameter (MWD), total carbon in macroaggregates (Ct 250), total carbon in large microaggregates (Ct 250--53), total carbon in small microaggregates (Ct 53), nitrogen in macroaggregates (Nt 250), nitrogen in large microaggregates (Nt 250--53), nitrogen in small microaggregates (Nt 53), sodium, potassium, chloride, nitrate, sulfate, pH, and electrical conductivity (EC).
	}
	\label{fig:M3-F8}
\end{figure}

### 2025-04-08 tex/Manuscript-4.tex
Update manuscript files with chapter marks and improve section formatting for clarity
Add titles to figures and tables

\chapter{Microbially induced soil aggregate turnover across different climates and moisture regimes}
\label{chap:manuscript4} % Label for potential cross-referencing (start page)

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=1\textwidth]{img/M4-Figure_1.png}
	\caption{Location of the four study sites along the climate gradient on the Chilean Coastal Cordillera. MAP, mean annual precipitation; MAT, mean annual temperature.}
	\label{fig:M4-F1}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=1\textwidth]{img/M4-Figure_2.png}
	\caption{Soil properties in native soils (+) and sterilized soils (-) of different climates. 
    A) Aggregate size distribution. 
    B) SOC content, 
    C) TN content, and 
    D) C/N ratio per aggregate class. 
    MAC, macroaggregate fraction \SIrange{250}{2000}{\micro\metre}; 
    MIC, microaggregate fraction \SIrange{20}{250}{\micro\metre}; 
    SC, silt/clay fraction \SI{< 20}{\micro\metre}. 
    Significant differences between native and sterilized soils are indicated by asterisks (* \(p < 0.05\); ** \(p < 0.01\)).}
	\label{fig:M4-F2}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=1\textwidth]{img/M4-Figure_3.png}
	\caption{Soil properties and microbial community structure in soils of different climates. A) Principal Component Analysis of soil properties in native soils (squares) and sterilized soils (circles) including MWD, TOC, soil aggregates, SOC, TN and C/N per aggregate size class. B) Canonical correspondence analysis of the ASV composition including soil properties: MWD, aggregate class (MAC, MIC, SC) and the respective C/N ratio, SOC and TN content. R0-R6; number of W-D repetitions; CM, constant moisture. Colors represent different climatic conditions.}
	\label{fig:M4-F3}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=1\textwidth]{img/M4-Figure_4.jpg}
	\caption{Principal Component Analyses of soil properties in native soils (squares) and sterilized soils (circles) including significant soil properties. A) arid, B) semi-arid, C) mediterranean and D) humid site. Microbial influence is indicated by sample separation along the x-axis.}
	\label{fig:M4-F4}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=1\textwidth]{img/M4-Figure_5.jpg}
	\caption{Prokaryotic and fungal abundance as well as prokaryotic diversity in soil material from different climates. A) 16S and 28S rRNA gene abundances of bacteria, archaea and fungi. Bacterial and archaeal diversity based on B) Shannon and C) Chao-1 diversity indices. R0 - R6, number of W-D repetitions; CM, constant moisture}
	\label{fig:M4-F5}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=1\textwidth]{img/M4-Figure_6.png}
	\caption{Relative abundance of prokaryotic families in soil material from different climates and after different soil treatments. R0-R6; number of W-D repetitions; CM, constant moisture. Each bubble represents the mean relative abundance of technical replicates.}
	\label{fig:M4-F6}
\end{figure}

>>>>

\chapter{Microbially induced soil aggregate turnover across different climates and moisture regimes}
\chaptermark{Manuscript 4}
\label{chap:manuscript4} % Label for potential cross-referencing (start page)

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=1\textwidth]{img/M4-Figure_1.png}
	\caption[Location of the four study sites along the climate gradient on the Chilean Coastal Cordillera]{Location of the four study sites along the climate gradient on the Chilean Coastal Cordillera. MAP, mean annual precipitation; MAT, mean annual temperature.}
	\label{fig:M4-F1}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=1\textwidth]{img/M4-Figure_2.png}
	\caption[Soil properties in native soils and sterilized soils of different climates]{Soil properties in native soils (+) and sterilized soils (-) of different climates. 
    A) Aggregate size distribution. 
    B) SOC content, 
    C) TN content, and 
    D) C/N ratio per aggregate class. 
    MAC, macroaggregate fraction \SIrange{250}{2000}{\micro\metre}; 
    MIC, microaggregate fraction \SIrange{20}{250}{\micro\metre}; 
    SC, silt/clay fraction \SI{< 20}{\micro\metre}. 
    Significant differences between native and sterilized soils are indicated by asterisks (* \(p < 0.05\); ** \(p < 0.01\)).}
	\label{fig:M4-F2}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=1\textwidth]{img/M4-Figure_3.png}
	\caption[Soil properties and microbial community structure in soils of different climates]{Soil properties and microbial community structure in soils of different climates. A) Principal Component Analysis of soil properties in native soils (squares) and sterilized soils (circles) including MWD, TOC, soil aggregates, SOC, TN and C/N per aggregate size class. B) Canonical correspondence analysis of the ASV composition including soil properties: MWD, aggregate class (MAC, MIC, SC) and the respective C/N ratio, SOC and TN content. R0-R6; number of W-D repetitions; CM, constant moisture. Colors represent different climatic conditions.}
	\label{fig:M4-F3}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=1\textwidth]{img/M4-Figure_4.jpg}
	\caption[Principal Component Analyses of soil properties in native soils and sterilized soils including significant soil properties]{Principal Component Analyses of soil properties in native soils (squares) and sterilized soils (circles) including significant soil properties. A) arid, B) semi-arid, C) mediterranean and D) humid site. Microbial influence is indicated by sample separation along the x-axis.}
	\label{fig:M4-F4}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=1\textwidth]{img/M4-Figure_5.jpg}
	\caption[Prokaryotic and fungal abundance as well as prokaryotic diversity in soil material from different climates]{Prokaryotic and fungal abundance as well as prokaryotic diversity in soil material from different climates. A) 16S and 28S rRNA gene abundances of bacteria, archaea and fungi. Bacterial and archaeal diversity based on B) Shannon and C) Chao-1 diversity indices. R0 - R6, number of W-D repetitions; CM, constant moisture}
	\label{fig:M4-F5}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=1\textwidth]{img/M4-Figure_6.png}
	\caption[Relative abundance of prokaryotic families in soil material from different climates and after different soil treatments]{Relative abundance of prokaryotic families in soil material from different climates and after different soil treatments. R0-R6; number of W-D repetitions; CM, constant moisture. Each bubble represents the mean relative abundance of technical replicates.}
	\label{fig:M4-F6}
\end{figure}

### 2025-04-08 tex/Manuscript-5.tex
Update manuscript files with chapter marks and improve section formatting for clarity
Add titles to figures and tables

\chapter{Living and decaying roots as regulators of soil aggregation and organic matter formation---from the rhizosphere to the detritusphere}
\label{chap:manuscript5} % Label for potential cross-referencing (start page)

@@

  \caption{Elemental and isotopic composition of above- and belowground biomass. Relative amounts of carbohydrates, proteins, lignin, lipids, and carbonyls from two incubation phases in topsoil and subsoil. Asterisks denote significance ($\bullet$ $p < 0.1$, *$p < 0.05$, **$p < 0.01$, ***$p < 0.001$).}

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=1\textwidth]{img/M5-Figure_1.png}
	\caption{C and N contents in water-stable aggregate size classes. The contents of a) C and b) N (in \si{mg\,\gram^{-1}}\,fraction) in three water-stable aggregate-size classes and the concentrations of c) C and d) N (in \si{mg\,\gram^{-1}}\,soil) in the bulk soil. Green represents a living root phase (rhizosphere) and brown a decaying root phase (detritusphere) together with corresponding controls. Asterisks denote significant differences between rooted and control samples (\(.P < 0.1\), *\(P < 0.05\), **\(P < 0.01\), ***\(P < 0.001\)). Bars represent means \(\pm\)SD (\(n=6\) independent replicates).}
	\label{fig:M5-F1}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=1\textwidth]{img/M5-Figure_2.png}
	\caption{C and N contents in and contributions of particulate organic matter fractions. The content of a) C and b) N (in \si{mg\,\gram^{-1}}\,soil) and the contribution of c) C and d) N to the total stock (in \%) of organic matter fractions (fPOM, oPOM and oPOM<\SI{20}{\micro\metre}). Green represents a living root phase (rhizosphere) and brown a decaying root phase (detritusphere) together with corresponding controls in faded colors. Asterisks denote significant differences between rooted and control samples (\(.P < 0.1\), *\(P < 0.05\), **\(P < 0.01\), ***\(P < 0.001\)). Bars represent means \(\pm\)SD (\(n=3\) independent replicates).}
	\label{fig:M5-F2}
\end{figure}

@@

\begin{figure}[H] % Requires float package
  \centering
  \includegraphics[width=1\textwidth]{img/M5-Figure_3.png} % Requires graphicx
  \caption{PLFA profiling of microbial community structure. The a) total content of extracted fatty acids (in \si{nmol\,C\text{-}FA\,\gram^{-1}}), the content of markers associated with b) fungi (\si{nmol\,C\text{-}FA\,\gram^{-1}}) and c) bacteria (\si{nmol\,C\text{-}FA\,\gram^{-1}}) and the d) fungi:bacteria ratio and e) $\text{Gram}^{+}:\text{Gram}^{-}$ ratio in a topsoil and subsoil. Green boxes represent the living root phase (rhizosphere) and brown the decaying root phase (detritusphere) together with corresponding controls in faded colors. Asterisks denote significant differences between rooted and control samples (\textbullet\(P < 0.1\), *\(P < 0.05\), **\(P < 0.01\), ***\(P < 0.001\)). Box plots indicate medians (line) and means (x), where the first (Q1) and third (Q3) quartile are represented by the lower, respectively upper bounds of the box. Error bars represent the data range, bounded to \(1.5 \times (\text{Q3}-\text{Q1})\); (\(n = 6\) independent replicates).} % Requires siunitx, amsmath
  \label{fig:M5-F3} % Label placed after caption
\end{figure}

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=1\textwidth]{img/M5-Figure_4.png}
	\caption{a) Living roots fostered the formation of macroaggregates in both topsoil and subsoil, and b) induced a change in the microbial community composition in the subsoil towards a higher relative abundance of fungi. This was not reflected in the topsoil, where c) the microbial abundance instead increased uniformly in the rhizosphere without structural changes in the community. While the increased total microbial abundance was maintained in the detritusphere, the composition changed as Gram+ bacteria outcompeted fungi. Around decaying roots in the topsoil, d) OM was protected in aggregates via the formation of occluded POM (oPOM<\SI{20}{\micro\metre}) and in the subsoil, e) the slower microbial C turnover resulted in an accumulation of fresh C inputs in highly bioavailable forms (fPOM) around both living and decaying roots. While the root-induced macroaggregates persisted after plant death in the topsoil, f) the aggregates disintegrated in the subsoil around the decaying roots.}
	\label{fig:M5-F4}
\end{figure}

>>>>

\chapter{Living and decaying roots as regulators of soil aggregation and organic matter formation---from the rhizosphere to the detritusphere}
\chaptermark{Manuscript 5}
\label{chap:manuscript5} % Label for potential cross-referencing (start page)

@@

  \caption[Elemental and isotopic composition of above- and belowground biomass]{Elemental and isotopic composition of above- and belowground biomass. Relative amounts of carbohydrates, proteins, lignin, lipids, and carbonyls from two incubation phases in topsoil and subsoil. Asterisks denote significance ($\bullet$ $p < 0.1$, *$p < 0.05$, **$p < 0.01$, ***$p < 0.001$).}

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=1\textwidth]{img/M5-Figure_1.png}
	\caption[C and N contents in water-stable aggregate size classes]{C and N contents in water-stable aggregate size classes. The contents of a) C and b) N (in \si{mg\,\gram^{-1}}\,fraction) in three water-stable aggregate-size classes and the concentrations of c) C and d) N (in \si{mg\,\gram^{-1}}\,soil) in the bulk soil. Green represents a living root phase (rhizosphere) and brown a decaying root phase (detritusphere) together with corresponding controls. Asterisks denote significant differences between rooted and control samples (\(.P < 0.1\), *\(P < 0.05\), **\(P < 0.01\), ***\(P < 0.001\)). Bars represent means \(\pm\)SD (\(n=6\) independent replicates).}
	\label{fig:M5-F1}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=1\textwidth]{img/M5-Figure_2.png}
	\caption[C and N contents in and contributions of particulate organic matter fractions]{C and N contents in and contributions of particulate organic matter fractions. The content of a) C and b) N (in \si{mg\,\gram^{-1}}\,soil) and the contribution of c) C and d) N to the total stock (in \%) of organic matter fractions (fPOM, oPOM and oPOM<\SI{20}{\micro\metre}). Green represents a living root phase (rhizosphere) and brown a decaying root phase (detritusphere) together with corresponding controls in faded colors. Asterisks denote significant differences between rooted and control samples (\(.P < 0.1\), *\(P < 0.05\), **\(P < 0.01\), ***\(P < 0.001\)). Bars represent means \(\pm\)SD (\(n=3\) independent replicates).}
	\label{fig:M5-F2}
\end{figure}

@@

\begin{figure}[H] % Requires float package
  \centering
  \includegraphics[width=1\textwidth]{img/M5-Figure_3.png} % Requires graphicx
  \caption[PLFA profiling of microbial community structure]{PLFA profiling of microbial community structure. The a) total content of extracted fatty acids (in \si{nmol\,C\text{-}FA\,\gram^{-1}}), the content of markers associated with b) fungi (\si{nmol\,C\text{-}FA\,\gram^{-1}}) and c) bacteria (\si{nmol\,C\text{-}FA\,\gram^{-1}}) and the d) fungi:bacteria ratio and e) $\text{Gram}^{+}:\text{Gram}^{-}$ ratio in a topsoil and subsoil. Green boxes represent the living root phase (rhizosphere) and brown the decaying root phase (detritusphere) together with corresponding controls in faded colors. Asterisks denote significant differences between rooted and control samples (\textbullet\(P < 0.1\), *\(P < 0.05\), **\(P < 0.01\), ***\(P < 0.001\)). Box plots indicate medians (line) and means (x), where the first (Q1) and third (Q3) quartile are represented by the lower, respectively upper bounds of the box. Error bars represent the data range, bounded to \(1.5 \times (\text{Q3}-\text{Q1})\); (\(n = 6\) independent replicates).} % Requires siunitx, amsmath
  \label{fig:M5-F3} % Label placed after caption
\end{figure}

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=1\textwidth]{img/M5-Figure_4.png}
	\caption[Conceptual diagram illustrating how living and decaying roots drive macroaggregate formation, organic matter protection, and microbial community shifts from the rhizosphere to the detritusphere in topsoil and subsoil]{a) Living roots fostered the formation of macroaggregates in both topsoil and subsoil, and b) induced a change in the microbial community composition in the subsoil towards a higher relative abundance of fungi. This was not reflected in the topsoil, where c) the microbial abundance instead increased uniformly in the rhizosphere without structural changes in the community. While the increased total microbial abundance was maintained in the detritusphere, the composition changed as Gram+ bacteria outcompeted fungi. Around decaying roots in the topsoil, d) OM was protected in aggregates via the formation of occluded POM (oPOM<\SI{20}{\micro\metre}) and in the subsoil, e) the slower microbial C turnover resulted in an accumulation of fresh C inputs in highly bioavailable forms (fPOM) around both living and decaying roots. While the root-induced macroaggregates persisted after plant death in the topsoil, f) the aggregates disintegrated in the subsoil around the decaying roots.}
	\label{fig:M5-F4}
\end{figure}

### 2025-04-08 tex/Methodology.tex
Refactor manuscript formatting and update author contributions
- Revised the title and author section in Manuscript 5 for improved clarity and presentation.
- Adjusted spacing and formatting for better visual alignment.
- Updated author contribution descriptions to a more concise format.
- Changed the bibliography style reference in Manuscript 5 to 'literatur_all_clean'.
- Removed auxiliary files for Methodology, Publications, and Results_Discussion to clean up the project structure.
- Updated statistical analysis references in Methodology.tex to reflect the latest citations.
Add titles to fig

\begin{figure}[H]
	\centering
	\includegraphics[width=1\textwidth]{img/location-map.png}
	\caption{Location of study sites relative to South America. From north to south: Pan de Azúcar (PdA), Santa Gracia (SG), Quebrada de Talca (QdT), La Campana (LC), and Nahuelbuta (NA).}
	\label{fig:location-map}
\end{figure}

@@

\begin{figure}[h!]
	\centering
	\includegraphics[width=1\textwidth]{img/location-panel.png}
	\caption{General view (a, c, d, g, and i) and sampled biocrust (b, d, f, h, and j) of PdA, SG, QdT, LC, and NA.}
	\label{fig:location-panel}
\end{figure}

@@

\begin{figure}[h!]
	\centering
	\includegraphics[width=1\textwidth]{img/sampling-panel.png}
	\caption{Construction diagram of the soil erosion flux box used in the experiment (a), general view of a plot with the presence of biocrust prior to sampling (b). (c, d) shows an installed cutting frame and the cleared and prepared soil. (e) demonstrates the setting for rainfall simulations at the Nahuelbuta (NA) study site.}
	\label{fig:sampling-panel}
\end{figure}

@@

Analysis of variance (ANOVA) and analysis of covariance (ANCOVA) were also employed, particularly to assess differences in measured properties between treatments and across sites or horizons. Where applicable, soil baseline variables were used as covariates in ANCOVA (Manuscripts 2 and 5). Non-parametric tests, such as the Kruskal-Wallis test followed by Mann-Whitney post-hoc tests, were used when normality or homoscedasticity assumptions were violated (Manuscript 3). Data transformations were applied when necessary, using the $bestNormalize$ package \citep{Peterson2019,Peterson2020}. The Dunn-Šidák correction was implemented for multiple comparisons \citep{Hothorn2008}.

>>>>

\begin{figure}[H]
	\centering
	\includegraphics[width=1\textwidth]{img/location-map.png}
	\caption[Location of study sites relative to South America]{Location of study sites relative to South America. From north to south: Pan de Azúcar (PdA), Santa Gracia (SG), Quebrada de Talca (QdT), La Campana (LC), and Nahuelbuta (NA).}
	\label{fig:location-map}
\end{figure}

@@

\begin{figure}[h!]
	\centering
	\includegraphics[width=1\textwidth]{img/location-panel.png}
	\caption[General view and biocrust sampled for the study sites]{General view (a, c, d, g, and i) and sampled biocrust (b, d, f, h, and j) of PdA, SG, QdT, LC, and NA.}
	\label{fig:location-panel}
\end{figure}

@@

\begin{figure}[h!]
	\centering
	\includegraphics[width=1\textwidth]{img/sampling-panel.png}
	\caption[Field experimental setup for soil erosion and rainfall simulation: construction of the flux box, plot preparation, and biocrust evaluation at Nahuelbuta (NA)]{Construction diagram of the soil erosion flux box used in the experiment (a), general view of a plot with the presence of biocrust prior to sampling (b). (c, d) shows an installed cutting frame and the cleared and prepared soil. (e) demonstrates the setting for rainfall simulations at the Nahuelbuta (NA) study site.}
	\label{fig:sampling-panel}
\end{figure}

@@

Analysis of variance (ANOVA) and analysis of covariance (ANCOVA) were also employed, particularly to assess differences in measured properties between treatments and across sites or horizons. Where applicable, soil baseline variables were used as covariates in ANCOVA (Manuscripts 2 and 5). Non-parametric tests, such as the Kruskal-Wallis test followed by Mann-Whitney post-hoc tests, were used when normality or homoscedasticity assumptions were violated (Manuscript 3). Data transformations were applied when necessary, using the $bestNormalize$ package \citep{Peterson2021,Peterson2020}. The Dunn-Šidák correction was implemented for multiple comparisons \citep{Hothorn2008}.
